Ode to Reviewer Two

### 2016-03-08 ode/ode.tex
fix meter of many lines in ode

\noindent
My paper submitted, the deadline complete;\\
The product of months of lonely toil,\\
With quality prose and experiments replete\\
Amid insecurities, fears, and other turmoil.\\
Though once I feared a harsh rejection,\\
My advisor assured me that my proofs were sound\\
And my treatment of the work related, fair,\\
So I've come to believe in the paper's perfection.\\
Through this research, new self-confidence found,\\
Though all-nighters have left me exhausted and drowned.\\
Now waiting for judgement from reviewers elsewhere.\\
\\
But alas! Though first and third reviewers were happy,\\
Reviewer the second couldn't seem to accept.\\
He gave reasons he thought my paper was crappy,\\
But I found his attempted critique most inept.\\
His comments betrayed a misunderstanding\\
And nonsense ``suggestions'' were falsely polite,\\
Completely missing the point of my work.\\
I couldn't believe what he was demanding:\\
To re-run experiments, perhaps out of spite;\\
An unrelated paper he asked me to cite!\\
(Probably his own.) What a jerk.\\
\\
With a glimmer of hope, I wrote a rebuttal\\
Appealing to reviewers One and Three impressed,\\
And suggested to Two, hey, you missed something subtle?\\
You'll reconsider, I desp'rately expressed.\\
The final suggestions were naught but derision:\\
``Clearly elaborate!'' was all Two replied,\\
Hiding the true message that he was outwit;\\
But it was too late to change their decision.\\
My paper rejected, my joy and pride,\\
My confidence collapsed in a sudden landslide;\\
Now to find somewhere to resubmit.\\

>>>>

\noindent
My paper submitted, the deadline complete;\\
The product of months of lonely toil,\\
With quality prose and exper'ments replete\\
Amid insecurities and other turmoil.\\
Though once I feared a harsh rejection,\\
My advisor assured me my proofs were quite sound\\
And my treatment of the work related, fair.\\
So I've come to believe in the paper's perfection;\\
Though all-nighters have left me exhausted and drowned,\\
Through this research, new self-esteem found!\\
Now waiting for judgment from reviewers elsewhere.\\
\\
Alas! Though readers first and third were happy,\\
Reviewer the second couldn't bear to accept.\\
He gave several reasons my paper seemed crappy,\\
But I found his attempted critique most inept.\\
His comments betrayed a misunderstanding\\
And nonsense `suggestions' were falsely polite,\\
Completely missing the point of my work.\\
I couldn't believe what he was demanding:\\
To rerun my test suite, perhaps out of spite;\\
An unr'lated paper he asked me to cite!\\
(Probably his own.) What an arrogant jerk.\\
\\
With a glimmer of hope, I wrote a rebuttal\\
Appealing to readers One and Three impressed,\\
And suggested to Two, ``Hey, you missed something subtle?\\
You'll reconsider,'' I desp'rately expressed.\\
The final suggestions were naught but derision:\\
``Clearly elaborate!'' was all Two replied,\\
Hiding the plain truth that he'd been outwit.\\
For it was too late to change their decision:\\
My paper rejected, my joy and my pride,\\
My conf'dence collapsed in a sudden landslide.\\
Now to find somewhere to soon resubmit.\\
